\documentclass[10pt,a4paper]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel}

% adjust the page margins
\usepackage[scale=0.75, left=2cm, right=2cm, top=1.5cm, bottom=1cm]{geometry}

\moderncvtheme[blue]{classic}

% personal data
\name{Mathieu}{\bsc{Soum}}
\title{Software architect \& developer}
\address{180 avenue de la Gloire\\}{31500 \bsc{Toulouse, France}}
\mobile{+33 673 503 387}
\email{mathieu@soum.me}
\extrainfo{Driving licence / Personal vehicle}
\social[github]{Mathsoum}
\social[linkedin]{mathsoum}

\begin{document}
\maketitle
\section{Experiences}
\cventry{September 2015 --}{Software developer / Permanent contract}{Aboard Engineering}{Toulouse}
{France}{Missions :
\begin{itemize}
  \item{Continuation of the work on the plateform (see previous internship) ;}
  \item{Engine management functions development (C) ;}
  \item{Desktop GUI applications to monitor and manage custom hardware through CAN (C++/Qt, Peak Systems) ;}
  \item{MATLAB scripts processing Simulink models ;}
  \item{Python scripts for parsing/building XML documents ;}
  \item{IT equipment management ;}
  \item{System administration and server management (Linux Debian).}
\end{itemize}}
\cventry{November 2014 -- July 2015}{Software developer / Internship}{Aboard Engineering}{Toulouse}
{France}{Development of a rapid prototyping platform for engine management functions (Java/Swing).}
\cventry{May -- July 2014}{Grails developer / Internship}{Ticetime}{Toulouse}{France}{Contribution to a web based course content editor for teachers and researchers (Groovy/Grails).}
\cventry{May -- June 2013}{Java developer / Internship}{Toulouse's IT research institute (IRIT)}{Toulouse}{France}{Development of an application communicating with a building simulation software for a multi-agent system managing energy regulation (home automation).}
\cventry{December 2012}{Project management and software development}{Paul
Sabatier University}{Toulouse}{France}{Participation to the ``Nuit de l'Informatique'', 2012 edition.}
\cventry{July 2012}{C++ development, System administration / Temporary contract}{Memobox/2G
Technologies}{Toulouse}{France}{Porting of this same client (see previous intership) onto a Unix based system (FreeBSD). Integration of the client onto an embedded telecom acquisition probe.}
\cventry{April -- June 2012}{C++ Developer / Internship}{Memobox/2G Technologies}
{Toulouse}{France}{Development of a C++ desktop client to acquire multi-protocol and multi-platform telecom data for auditing purposes.}
\section{Formations}
\cvline{2013 -- 2015}{IT Master's Degree, specialization  in software development\newline Student project: Contribution to the open source KAddressBook software from the KDE project (C++/Qt, Git, Agile).
  \newline{\em Paul Sabatier University, Toulouse, France} }
\cvline{2012 -- 2013}{IT Bachelor's Degree.\newline Modules : Software testing and maintenance, Software developement methodology, Logical programing (Prolog)\newline {\em Paul Sabatier University, Toulouse, France} }
\cvline{2010 -- 2012}{IT DUT graduate.\newline Modules : Buisness creation, Java GUI design\newline Student project : Creation of a UML 2.0 graphical library (Java Swing)\newline{\em IUT 'A' Paul Sabatier, Toulouse, France} }
\cvline{2010}{High school diploma, specialization in engineering.
\newline {\em Paul Mathou High School, Gourdan-Polignan, France} }

\section{Voluntary activities}
\cventry{December 2015/14/13}{Voluntary activity}{Paul Sabatier University}{Toulouse}{France}{Member of the organization team of the ``Nuit De l'Info'' (\url{https://www.nuitdelinfo.com/}).}
\newpage

\section{Software Skills}
\cvcomputer{Design}{Merise, UML2.0}{DB}{MySQL, SQLite, MongoDB}
\cvcomputer{Languages}{C/C++ (Qt, POCO)\\Java (Swing, JNI)}{Redaction}{\LaTeX}
\cvcomputer{Script}{Bash\\Python (Tkinter \& system)}{Web}{Flask, Django}
\cvcomputer{Other skills}{Caml -- Prolog -- MATLAB}{}{}

\section{Langue skills}
\cvlanguage{French}{fluent}{}
\cvlanguage{English}{written, read, spoken}{}
\cvlanguage{Spanish}{notions}{}

\section{Interests}
\cvline{Software}{FOSS culture (attendee to workshops and conferences on open source software).}
\cvline{Hobbies}{Card games, board games, astronomy (amateur).}

\end{document}
